### 2025-02-26 paper/performance.tex
Minor tweaks.

PyTorch version result in extremely high runtime of 19 and 61 seconds,
and we observer low GPU utilization.  While this is likely to be a problem
with a system configuration, we report these numbers here as an indication
that performance of machine learning systems is fragile.

@@

\begin{table}
\begin{tabular}{crrrr}
\textbf{Size of training set} & \multicolumn{3}{c}{\textbf{Runtime}} & \textbf{Ratio} \\
& Futhark & TensorFlow & \\
$10000$ & $0.91s$ & $1.07s$ &  $0.85\times{}$ \\
$60000$ & $4.93s$ & $2.92s$ &  $1.68\times{}$
\end{tabular}
\caption{Training time for various training set sizes, comparing
  Futhark, Tensorflow, and PyTorch, running on an A100 GPU. The final column
  shows the speedup of TensorFlow compared to Futhark. We use a batch
  size of $1000$, a training rate of $0.05$, and train for $10$
  epochs.}
\label{tab:performance}
\end{table}

>>>>

Our PyTorch version results in extremely high runtimes of 19 and 61
seconds, and we observe low GPU utilization. While this is likely to
be a problem with a system configuration, we report these numbers here
as an indication that performance of machine learning systems is
fragile.

@@

\begin{table}
\begin{tabular}{crrr}
\textbf{Size of training set} & \multicolumn{2}{c}{\textbf{Runtime}} & \textbf{Ratio} \\
& Futhark & TensorFlow & \\
$10000$ & $0.91s$ & $1.07s$ &  $0.85\times{}$ \\
$60000$ & $4.93s$ & $2.92s$ &  $1.68\times{}$
\end{tabular}
\caption{Training time for various training set sizes, comparing
  Futhark, Tensorflow, and PyTorch, running on an A100 GPU. The final column
  shows the speedup of TensorFlow compared to Futhark. We use a batch
  size of $1000$, a training rate of $0.05$, and train for $10$
  epochs.}
\label{tab:performance}
\end{table}
